An Experimental Evaluation of Hybrid Vector Search (EA\&B)

### 2025-04-27 VLDB2026/main.tex
Update main.tex

		\begin{subfigure}{\columnwidth}
			\centering
			\setlength{\abovecaptionskip}{0cm}
			\setlength{\belowcaptionskip}{-0.1cm}
			\includegraphics[width=0.95\linewidth]{figures/indexData/exp_7_build_time_comparison_query1.pdf}
			\caption{Index construction time}
			\label{fig:build_time_comparison_query1}
		\end{subfigure}

		\begin{subfigure}{\columnwidth}
			\centering
			\setlength{\abovecaptionskip}{0cm}
			\setlength{\belowcaptionskip}{-0.1cm}
			\includegraphics[width=0.95\linewidth]{figures/indexData/exp_7_index_size_mb_comparison_query1.pdf}
			\caption{Index size}
			\label{fig:index_size_mb_comparison_query1}
		\end{subfigure}

		\begin{subfigure}{\columnwidth}
			\centering
			\setlength{\abovecaptionskip}{0cm}
			\setlength{\belowcaptionskip}{-0.3cm}
			\includegraphics[width=0.95\linewidth]{figures/indexData/exp_7_memory_mb_comparison_query1.pdf}
			\caption{Peak memory usage}
			\label{fig:memory_mb_comparison_query1}
		\end{subfigure}

		\caption{Time and space overhead of attribute filtering index construction}
		\label{fig:build_index_comparison}
	\end{figure}

@@

	\begin{figure*}
		\centering
		    \setlength{\abovecaptionskip}{0cm}
		    \setlength{\belowcaptionskip}{-0.4cm}
		\includegraphics[width=\textwidth]{figures/exp/exp_6_1.pdf}
		\caption{Effect of dataset on Query}
		\label{fig:exp_6_1}
	\end{figure*}

@@

	\begin{figure}[t]
		\centering
		\setlength{\abovecaptionskip}{0.02cm}
		\setlength{\belowcaptionskip}{0.02cm}
		\hspace*{11pt}
		% 放大的图例（占满单栏）
		\includegraphics[width=0.93\columnwidth]{figures/indexData/rangeFilter_legend_only.pdf}

@@

		% 三图横排
		\begin{subfigure}[t]{0.32\columnwidth}
			\centering
			\setlength{\abovecaptionskip}{0.02cm}
			\setlength{\belowcaptionskip}{0.02cm}
			\includegraphics[width=\linewidth]{figures/indexData/rangeFilter_build_time_comparison_query.pdf}
			\caption{Index construction time}
			\label{fig:rangeFilter_build_time}
		\end{subfigure}
		\hfill
		\begin{subfigure}[t]{0.32\columnwidth}
			\centering
			\setlength{\abovecaptionskip}{0.02cm}
			\setlength{\belowcaptionskip}{0.02cm}
			\includegraphics[width=\linewidth]{figures/indexData/rangeFilter_index_size_mb_comparison_query.pdf}
			\caption{Index size}
			\label{fig:rangeFilter_index_size_mb}
		\end{subfigure}
		\hfill
		\begin{subfigure}[t]{0.32\columnwidth}
			\centering
			\setlength{\abovecaptionskip}{0.02cm}
			\setlength{\belowcaptionskip}{0.02cm}
			\includegraphics[width=\linewidth]{figures/indexData/rangeFilter_memory_mb_comparison_query.pdf}
			\caption{Peak memory usage}
			\label{fig:rangeFilter_memory_mb}
		\end{subfigure}

		\caption{Time and space overhead of range filtering index construction}
		\label{fig:rangeFilter_build_index_comparison}
	\end{figure}

@@

	\textit{\textbf{Index construction time.}}
	Figure~\ref{fig:rangeFilter_build_time} shows the single-threaded index construction time. Faiss builds the index fastest. Because Faiss obtains subsamples through sampling and then calculates the cluster centroid, the computational complexity is significantly reduced.

@@

	\begin{figure*}[htbp]
		\centering
		  \setlength{\abovecaptionskip}{0cm}
		    \setlength{\belowcaptionskip}{-0.5cm}
		\includegraphics[width=\textwidth]{figures/exp/exp_8_2.pdf}
		\caption{RF-ANN search }
		\label{fig:exp_8_2}
	\end{figure*}

@@

	% \begin{figure*}[htbp]
		%     \centering
		%     \setlength{\abovecaptionskip}{0cm}
		%     \setlength{\belowcaptionskip}{-0.4cm}
		%     \includesvg[width=\textwidth]{figures/exp/exp_8_3.svg}
		%     \caption{Dataset Effect on RF-ANN Search}
		%     \label{fig:exp_8_3}
		% \end{figure*}
	\begin{figure*}[htbp]
		\centering
		    \setlength{\abovecaptionskip}{0cm}
		    \setlength{\belowcaptionskip}{-0.5cm}
		\includegraphics[width=\textwidth]{figures/exp/exp_8_3.pdf}
		\caption{Dataset Effect on RF-ANN Search}
		\label{fig:exp_8_3}
	\end{figure*}

@@

	\begin{table}[t]
		\centering
		\setlength{\abovecaptionskip}{0.05cm}
		\caption{Algorithm Recommendation per Scenario}
		\resizebox{\columnwidth}{!}{
			\begin{tabular}{|l|c|c|}
				\hline
				\textbf{Scenario} & \textbf{Attribute Filtering} & \textbf{Range Filtering}\\
				\hline
				S1: Large-scale Datasets & Puck, UNG & iRange\\
				\hline
				S2: Fast Index Construction & ACORN-1, UNG  &Faiss\\
				\hline
				S3: Query on Hard Datasets & CAPS, UNG &WinFilter, iRange, DSG\\
				\hline
				S4: Query on Easy Datasets & StitchedVamana, NHQ, UNG & WinFilter, iRange\\

				\hline
				S5: General-purpose Use & Milvus, Faiss &DSG, UNIFY\\
				\hline
				S6: Resource-constrained Environments & CAPS, Faiss&Faiss, SeRF \\
				\hline
				S7: High-Recall Querying & UNG & WinFilter \\
				\hline
				S8: OOD scenarios & UNG &WinFilter  \\
				\hline
			\end{tabular}
		}
		\label{tab:algo_scenarios}

@@

\textcolor{blue}{
In our experiments, we find that many range filtering algorithms perform worse than Faiss at high recall (0.95). This shows that the design of current algorithms still needs improvement. We suggest that future range filtering algorithms should include Faiss as a baseline.
}

>>>>

		\begin{subfigure}{\columnwidth}
			\centering
			\setlength{\abovecaptionskip}{-0.02cm}
			\setlength{\belowcaptionskip}{-0.1cm}
			\includegraphics[width=0.95\linewidth]{figures/indexData/exp_7_build_time_comparison_query1.pdf}
			\caption{Index construction time}
			\label{fig:build_time_comparison_query1}
		\end{subfigure}

		\begin{subfigure}{\columnwidth}
			\centering
			\setlength{\abovecaptionskip}{-0.02cm}
			\setlength{\belowcaptionskip}{-0.1cm}
			\includegraphics[width=0.95\linewidth]{figures/indexData/exp_7_index_size_mb_comparison_query1.pdf}
			\caption{Index size}
			\label{fig:index_size_mb_comparison_query1}
		\end{subfigure}

		\begin{subfigure}{\columnwidth}
			\centering
			\setlength{\abovecaptionskip}{-0.02cm}
			\setlength{\belowcaptionskip}{-0.3cm}
			\includegraphics[width=0.95\linewidth]{figures/indexData/exp_7_memory_mb_comparison_query1.pdf}
			\caption{Peak memory usage}
			\label{fig:memory_mb_comparison_query1}
		\end{subfigure}

%		\caption{Time and space overhead of attribute filtering index construction}
		\caption{\textcolor{red}{Time and space overhead of index construction}}
		\label{fig:build_index_comparison}
	\end{figure}

@@

	\begin{figure*}
		\centering
		    \setlength{\abovecaptionskip}{0cm}
		    \setlength{\belowcaptionskip}{-0.4cm}
		\includegraphics[width=0.97\textwidth]{figures/exp/exp_6_1.pdf}
		\caption{Effect of dataset on Query}
		\label{fig:exp_6_1}
	\end{figure*}

@@

	\begin{figure}[t]
		\centering

		\setlength{\abovecaptionskip}{0.02cm}
		\setlength{\belowcaptionskip}{-0.1cm}
		\hspace*{11pt}
		% 放大的图例（占满单栏）
		\includegraphics[width=0.93\columnwidth]{figures/indexData/rangeFilter_legend_only.pdf}

@@

		% 三图横排
		\begin{subfigure}[t]{0.32\columnwidth}
			\centering
			\captionsetup{font=small}
			\setlength{\abovecaptionskip}{0.02cm}
			\setlength{\belowcaptionskip}{0.02cm}
			\includegraphics[width=\linewidth]{figures/indexData/rangeFilter_build_time_comparison_query.pdf}
			\caption{\footnotesize Construction time}
			\label{fig:rangeFilter_build_time}
		\end{subfigure}
		\hfill
		\begin{subfigure}[t]{0.32\columnwidth}
			\centering
			\setlength{\abovecaptionskip}{0.02cm}
			\setlength{\belowcaptionskip}{0.02cm}
			\includegraphics[width=\linewidth]{figures/indexData/rangeFilter_index_size_mb_comparison_query.pdf}
			\caption{\footnotesize Index size}
			\label{fig:rangeFilter_index_size_mb}
		\end{subfigure}
		\hfill
		\begin{subfigure}[t]{0.32\columnwidth}
			\centering
			\setlength{\abovecaptionskip}{0.02cm}
			\setlength{\belowcaptionskip}{0.02cm}
			\includegraphics[width=\linewidth]{figures/indexData/rangeFilter_memory_mb_comparison_query.pdf}
			\caption{\footnotesize Peak memory usage}
			\label{fig:rangeFilter_memory_mb}
		\end{subfigure}

%		\caption{Time and space overhead of range filtering index construction}
		\caption{\textcolor{red}{Time and space overhead of index construction}}
		\label{fig:rangeFilter_build_index_comparison}
	\end{figure}

@@

	\textit{\textbf{Index construction time.}}
	Figure~\ref{fig:rangeFilter_build_time} shows the single-threaded index construction time. Faiss builds the index fastest. As Faiss obtains subsamples through sampling and calculates the cluster centroid, the computational complexity is significantly reduced.
%	shows the single-threaded index construction time. Faiss builds the index fastest. Because Faiss obtains subsamples through sampling and then calculates the cluster centroid, the computational complexity is significantly reduced.

@@

	\begin{figure*}[htbp]
		\centering
		  \setlength{\abovecaptionskip}{0cm}
		    \setlength{\belowcaptionskip}{-0.5cm}
		\includegraphics[width=0.95\textwidth]{figures/exp/exp_8_2.pdf}
		\caption{RF-ANN search }
		\label{fig:exp_8_2}
	\end{figure*}

@@

	% \begin{figure*}[htbp]
		%     \centering
		%     \setlength{\abovecaptionskip}{0cm}
		%     \setlength{\belowcaptionskip}{-0.4cm}
		%     \includesvg[width=\textwidth]{figures/exp/exp_8_3.svg}
		%     \caption{Dataset Effect on RF-ANN Search}
		%     \label{fig:exp_8_3}
		% \end{figure*}
	\begin{figure*}[htbp]
		\centering
		    \setlength{\abovecaptionskip}{0cm}
		    \setlength{\belowcaptionskip}{-0.5cm}
		\includegraphics[width=0.8\textwidth]{figures/exp/exp_8_3.pdf}
		\caption{Dataset Effect on RF-ANN Search}
		\label{fig:exp_8_3}
	\end{figure*}

@@

	\begin{table}[t]
		\centering
		\setlength{\abovecaptionskip}{0.0cm}
		\caption{Algorithm Recommendation per Scenario}
		\resizebox{\columnwidth}{!}{
			\begin{tabular}{|l|c|c|}
				\hline
				\textbf{Scenario} & \textbf{Attribute Filtering} & \textbf{Range Filtering}\\
				\hline
				S1: Large-scale Datasets & Puck, UNG & iRange\\
				\hline
				S2: Fast Index Construction & ACORN-1, UNG  &Faiss\\
				\hline
				S3: Query on Hard Datasets & CAPS, UNG &WinFilter, iRange, DSG\\
				\hline
				S4: Query on Easy Datasets & StitchedVamana, NHQ, UNG & WinFilter, iRange\\

				\hline
				S5: General-purpose Use & Milvus, Faiss &DSG, UNIFY\\
				\hline
				S6: Resource-constrained Environments & CAPS, Faiss&Faiss, SeRF \\
				\hline
				S7: High-Recall Querying & UNG & WinFilter \\
				\hline
				S8: OOD scenarios & UNG &WinFilter  \\
				\hline
			\end{tabular}
		}
		\label{tab:algo_scenarios}
	\vspace{-0.1cm}
	\end{table}

@@

\textcolor{blue}{
In our experiments, many range filtering algorithms perform worse than Faiss at high recall (0.95), showing that current algorithm designs still need improvement. We suggest future future range filtering algorithms include Faiss as a baseline.
%In our experiments, we find that many range filtering algorithms perform worse than Faiss at high recall (0.95). This shows that the design of current algorithms still needs improvement. We suggest that future range filtering algorithms should include Faiss as a baseline.
}
